`You Draw It': Implementation of visually fitted trends with \texttt{r2d3}

### 2022-07-05 2022-sdss-you-draw-it-manuscript.qmd
A couple more comments

@@

@@

# Future Work

In this work, we implemented and validated ‘You Draw It’ as a new method to measure the patterns we see in data. We demonstrated the use of generalized additive models to statistically model participant feedback data and generalized the analysis method to nonlinear trends. While technical details of the development process are presented here, we intend to create an R package designed for easy implementation of 'You Draw It' task plots in order to make this tool accessible to other researchers. Further investigation is necessary to implement this method with real data in order to facilitate scientific communication.

>>>>

\svp{Describe the experiment formally. Don't be afraid to quote Mosteller's paper if you think it's necessary. Focus on one set of plots from the Mosteller paper and one set of plots from our exponential stuff, so you're demonstrating linear and nonlinear analysis. Include basic demographics, and compare to Mosteller's paper - we also had a sample of highly educated individuals. Right now you have a very short summary, but you need to actually explain the full process behind it, with all of the details you'd expect from a full experimental writeup.}

@@

\svp{Explain why our method works so well here - you can actually test whether the PCA residuals are closer than the OLS residuals formally, where Mosteller et al just said "seems like". Your method also extends beyond OLS using GAMMs. Fully describe the models you fit - assumptions, equations, etc.}

@@

\svp{It's also worth remarking on the effectiveness of the spaghetti plots and GAMM plots for visual analysis of the results. Gotta keep pounding the "visual analytics is statistics" drum a bit :). }

# Conclusion

\svp{The data presented in this paper are part of a much broader experiment on the perception of log scales; while this paper focuses primarily on the computational implementation of the You Draw It method and its adaptation to testing graphics, we are currently finishing the analysis and description of the broader experiment, which uses this You Draw It method to assess user prediction of exponential trends.}

\svp{By introducing an interactive method for assessing eye-fit data summaries, along with an analysis method which allows us to test competing hypotheses to determine whether user responses are similar to particular statistical models, we have provided another tool for experimentally testing statistical charts. In the future, we hope to create an R package to more easily facilitate these types of user experiments, making this technique available to other researchers who may not be willing to tinker with JavaScript directly.}

\svp{As with any method for testing statistical graphics, there are a host of additional studies which would be useful to understand how users react to the You Draw It method and what parameters are most important for the researcher to control. One avenue of future exploration is to investigate the effect of axis limits on user anchoring. We know that the perceptual experience is heavily affected by anchoring to e.g. axis breaks, and we would expect that a similar anchoring effect might be present based on the limits of the plot and the amount of space in x and y provided for the user to draw.}

XXX add references to the anchoring bit XXX

# References

### 2022-07-05 2022-sdss-you-draw-it-manuscript.tex
A couple more comments

\begin{document}
\maketitle
\begin{abstract}
How do statistical regression results compare to intuitive, visually
fitted results? Fitting lines by eye through a set of points has been
explored since the 20th century. Common methods of fitting trends by eye
involve maneuvering a string, black thread, or ruler until the fit is
suitable, then drawing the line through the set of points. In 2015, the
New York Times introduced an interactive feature, called `You Draw It,'
where readers are asked to input their own assumptions about various
metrics and compare how these assumptions relate to reality. This
research is intended to implement `You Draw It', adapted from the New
York Times, as a way to measure the patterns we see in data.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\hypertarget{future-work}{%
\section{Future Work}\label{future-work}}

In this work, we implemented and validated `You Draw It' as a new method
to measure the patterns we see in data. We demonstrated the use of
generalized additive models to statistically model participant feedback
data and generalized the analysis method to nonlinear trends. While
technical details of the development process are presented here, we
intend to create an R package designed for easy implementation of `You
Draw It' task plots in order to make this tool accessible to other
researchers. Further investigation is necessary to implement this method
with real data in order to facilitate scientific communication.

>>>>

\begin{document}
\maketitle
\begin{abstract}
How do statistical regression results compare to intuitive, visually
fitted results? Fitting lines by eye through a set of points has been
explored since the 20th century. Common methods of fitting trends by eye
involve maneuvering a string, black thread, or ruler until the fit is
suitable, then drawing the line through the set of points. In 2015, the
New York Times introduced an interactive feature, called `You Draw It,'
where readers are asked to input their own assumptions about various
metrics and compare how these assumptions relate to reality. This
research is intended to implement `You Draw It', adapted from the New
York Times, as a way to measure the patterns we see in data.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

\svp{It's also worth remarking on the effectiveness of the spaghetti plots and GAMM plots for visual analysis of the results. Gotta keep pounding the "visual analytics is statistics" drum a bit :). }

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\svp{The data presented in this paper are part of a much broader experiment on the perception of log scales; while this paper focuses primarily on the computational implementation of the You Draw It method and its adaptation to testing graphics, we are currently finishing the analysis and description of the broader experiment, which uses this You Draw It method to assess user prediction of exponential trends.}

\svp{By introducing an interactive method for assessing eye-fit data summaries, along with an analysis method which allows us to test competing hypotheses to determine whether user responses are similar to particular statistical models, we have provided another tool for experimentally testing statistical charts. In the future, we hope to create an R package to more easily facilitate these types of user experiments, making this technique available to other researchers who may not be willing to tinker with JavaScript directly.}

\svp{As with any method for testing statistical graphics, there are a host of additional studies which would be useful to understand how users react to the You Draw It method and what parameters are most important for the researcher to control. One avenue of future exploration is to investigate the effect of axis limits on user anchoring. We know that the perceptual experience is heavily affected by anchoring to e.g. axis breaks, and we would expect that a similar anchoring effect might be present based on the limits of the plot and the amount of space in x and y provided for the user to draw.}

XXX add references to the anchoring bit XXX

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}
